Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-03-23 paper/ms.tex
updating tex file to clarify focc>1 and correting some typos

\begin{figure*}
\begin{center}
\includegraphics[width=0.85\textwidth]{likelyplot_1deg_total.png}
\end{center}
\caption{One and two dimensional projections of the posterior
  probability distributions of \mmin, \mmax and \focc as described in
  the label of each sub-figure.} 
\label{fig:like}
\end{figure*}

\subsection{Observational constraints}
\label{subsec:obs}
\citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
at $z\sim 3$  with equivalent widths of $\gtrsim$65\AA\ and a flux limit
of $2\times10^17{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
Using spectroscopy they found a 22\% contamination fraction.
Their observations cover 5 (out of 9) independent and co-spatial fields of the VLT LBG Redshift Survey (VLRS). 
The  total observed  area corresponds to 1.07$\rm deg^2$ that translates to
$\sim$80$^2\hMpc^2$ in a comoving scale. \citet{Bielby16} used the
NB497  narrow-band filter whose 77\AA FWHM and 154\AA FWTM correspond to a total observational depth of 44\hMpc  and 82\hMpc comoving, respectively.

@@

We use halo catalogs constructed with a Bound-Density-Maxima (BDM) algorithm. The catalogs were obtained from the publicly available
Multidark database  \footnote{{\tt
    http://www.multidark.org/MultiDark/}} \citep{MultiDark}. For each
halo in the box we extract its comoving position and mass. 
We focus our work on halos more massive than $1.54\times 10^{9}$\hMsun resolved with at least  $10$ particles.
%the reasons for this choice are explained in the next sub-section.

@@

\subsection{Exploring and selecting consistent models}

We use the angular correlation function to compare the observations with our mock catalogs. 
This is done trough a thorough exploration of the parameter space of the models ${\mathcal M}$  by  means of a Monte Carlo Markov Chain minimization using  the EMCEE python package \citep{emcee2013}.
We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ to vary between  $9.2$ up to $13.4$, corresponding to the halo mass range of the simulation at $z=3$. 
Given that the typical scatter  in $N_{\mathrm halos}$ is about 0.3 dex (i.e. about  a factor of 2), our parameter space is restricted to models where the median number of dark matter halos is larger than  $N_{\rm LAE}/3$. 
The MCMC exploration is done using a total of 24 seeds and 400
iterations (9600 models) to sample the posterior PDF,  $P(\mmin,
\mmax, f_{\rm occ}| \mathcal{M}) \propto \exp(-\chi_{\mathcal
  M}^2/2)$, with

@@

In Fig. \ref{fig:like} we present yhe one and two dimensional
projections of the posterior probability distributions of \mmin, \mmax
and \focc. We find that the \mmin and \mmax parameter space cannot be
tightly constrained mainly because of cosmic variance and the large
observational Poisonnian uncertainty in the ACF. We however found that
9.6$<\log \mmin<$11.0 and 10.9$<\log\mmax<$13.0.   We interestingly
find that \focc\ is basically completely determined by \mmin  going
from \focc$=$0.015 when $\log\mmin=$9.6 to \focc$=$0.30 when
$\log\mmin=$11.0
($\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$). We remark that
those models where $\log \focc>0.00$ ($\focc>1$) correspond  to models where the number density  of halos is smaller than the number of observed LAEs but are
still consistent because of the uncertainty in the median number
density of LAEs in the universe due to cosmic variance (see
Fig. \ref{fig:cosmicv0}).%in the number of dark matter halos along the
                         %mock fields

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.85\textwidth]{likelyplot_1deg_total.png}
\end{center}
\caption{One and two dimensional projections of the posterior
  probability distributions of \mmin, \mmax\ and \focc\ as described in
  the label of each sub-figure. We remark that
those models where $\log \focc>0.00$ ($\focc>1$) correspond  to models where the number density  of halos is smaller than the number of observed LAEs but are
still consistent because of the uncertainty in the median number
density of LAEs in the universe due to cosmic variance. See
Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
\label{fig:like}
\end{figure*}

\subsection{Observational constraints}
\label{subsec:obs}
\citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
at $z\sim 3$  with equivalent widths of $\gtrsim$65\AA\ and a flux limit
of $2\times10^{17}{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
Using spectroscopy they found a 22\% contamination fraction.
Their observations cover 5 (out of 9) independent and co-spatial fields of the VLT LBG Redshift Survey (VLRS). 
The  total observed  area corresponds to 1.07$\rm deg^2$ that translates to
$\sim$80$^2\hMpc^2$ in a comoving scale. \citet{Bielby16} used the
NB497  narrow-band filter whose 77\AA\ FWHM and 154\AA FWTM correspond to a total observational depth of 44\hMpc\  and 82\hMpc\ comoving, respectively.

@@

We use halo catalogs constructed with a Bound-Density-Maxima (BDM) algorithm. The catalogs were obtained from the publicly available
Multidark database  \footnote{{\tt
    http://www.multidark.org/MultiDark/}} \citep{MultiDark}. For each
halo in the box we extract its comoving position and mass. 
We focus our work on halos more massive than $1.54\times 10^{9}$\hMsun\ resolved with at least  $10$ particles.
%the reasons for this choice are explained in the next sub-section.

@@

\subsection{Exploring and selecting consistent models}
\label{subsec:explore}
We use the angular correlation function to compare the observations with our mock catalogs. 
This is done trough a thorough exploration of the parameter space of the models ${\mathcal M}$ by  means of a Monte Carlo Markov Chain minimization using  the EMCEE python package \citep{emcee2013}.
We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ to vary between $9.2$ up to $13.4$, corresponding to the halo mass range of the simulation at $z=3$. 
Given that the typical scatter  in $N_{\mathrm halos}$ is about 0.3 dex (i.e. about  a factor of 2), our parameter space is restricted to models where the median number of dark matter halos is larger than  $N_{\rm LAE}/3$. Because of this posibility of having $N_{\mathrm halos}$  smaller than $N_{\rm LAE}$ there will be some models where    $\focc\equivN_{\rm LAE}/N_{\mathrm halo}>1$. Those models only reflect the uncertainty in the number density of LAEs due to cosmic variance.

The MCMC exploration is done using a total of 24 seeds and 400
iterations (9600 models) to sample the posterior PDF,  $P(\mmin,
\mmax, f_{\rm occ}| \mathcal{M}) \propto \exp(-\chi_{\mathcal
  M}^2/2)$, with

@@

In Fig. \ref{fig:like} we present yhe one and two dimensional
projections of the posterior probability distributions of \mmin, \mmax
and \focc. We find that the \mmin and \mmax parameter space cannot be
tightly constrained mainly because of cosmic variance and the large
observational Poisonnian uncertainty in the ACF. We however found that
9.6$<\log \mmin<$11.0 and 10.9$<\log\mmax<$13.0.   We interestingly
find that \focc\ is basically completely determined by \mmin  going
from \focc$=$0.015 when $\log\mmin=$9.6 to \focc$=$0.30 when
$\log\mmin=$11.0
($\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$). We remark that
those models where $\log \focc>0.00$ ($\focc>1$) correspond  to models where the number density  of halos is smaller than the number of observed LAEs but are
still consistent because of the uncertainty in the median number
density of LAEs in the universe due to cosmic variance (see
Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore}).%in the number of dark matter halos along the
                         %mock fields
